\documentclass[a4paper,twoside, openany]{book}
%% "openany" allows for chapters on odd pages, it would leave a blank page otherwise, there is a script to build correct double paged stacked booklets, also, markdown generator
\usepackage[hmarginratio=1:1]{geometry}% equal left and right margins
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{varwidth}

\usepackage{xpatch}

\makeatletter

\xpatchcmd{\@makeschapterhead}{%
  \Huge \bfseries  #1\par\nobreak%
}{%
  \Huge \bfseries\centering #1\par\nobreak%
}{\typeout{Patched makeschapterhead}}{\typeout{patching of @makeschapterhead failed}}


\xpatchcmd{\@makechapterhead}{%
  \huge\bfseries \@chapapp\space \thechapter
}{%
  \huge\bfseries\centering \@chapapp\space \thechapter
}{\typeout{Patched @makechapterhead}}{\typeout{Patching of @makechapterhead failed}}

\makeatother

%% I just want stuff to be centered

\newenvironment{Verse}
  {\center\varwidth{\linewidth}\fontsize{18}{21.6}\selectfont}
  {\endvarwidth\endcenter}
%% verse but centered and bigger
\titleformat{\chapter}[display]
  {\normalfont\filcenter\bfseries}{}{0pt}{\Huge}
\renewcommand{\contentsname}{Table of Contents}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\usepackage[utf8]{inputenc}
\begin{document}
\font\mytitle=cmr12 at 40pt
\newcommand{\MONTH}{%
  \ifcase\the\month
  \or January% 1
  \or February% 2
  \or March% 3
  \or April% 4
  \or May% 5
  \or June% 6
  \or July% 7
  \or August% 8
  \or September% 9
  \or October% 10
  \or November% 11
  \or December% 12
  \fi}
%% Month of compilation
\title{\mytitle Alembic}
\author{Mattia Mascarello}
\date{}
%% I don't want that in the title
\frontmatter

\maketitle

\pagestyle{empty}
%% copyrightpage
\begingroup
\footnotesize
\parindent 0pt
\parskip \baselineskip
CC BY-SA 4.0 \the\year{} Mattia Mascarello\\

    Distribuited under the \href{https://creativecommons.org/licenses/by-sa/4.0/}{``Attribution-ShareAlike 4.0 International (CC BY-SA 4.0)"} license

    Poems by Mattia Mascarello


\vfill

\begin{center}
Anywhere the wind blows
\end{center}


\begin{center}
\begin{tabular}{ll}
Current Edition: \MONTH  \space \the\year
\end{tabular}
\end{center}

\vfill

Mattia Mascarello, \\
Alba (CN), Italy \\
\href{mailto:mattia.mascarello@outlook.it}{mattia.mascarello@outlook.it}\\
\href{https://github.com/MatMasIt}{Github}\\
\href{https://t.me/matmasak}{Telegram}



\vspace*{2\baselineskip}
\endgroup
\clearpage


%% inscription
\pagestyle{empty}
\begin{center}
Thanks to all of my friends.
\end{center}
\clearpage


%%preface
\pagestyle{empty}
\begin{center}
\textbf{Preface}\\
My stream of thought is stored in this container as I progress to read it
Essentially, a collection
\end{center}
\clearpage


%%empty page
\pagestyle{empty}
\begin{center}
\end{center}
\clearpage
\tableofcontents
\mainmatter


%% Start of poems

\chapter{Cogs}
\begin{Verse}
    Cogs of Ice\\
    Tick and Slide\\
    Subdivide the Time in Time\\
    Slow or steady to demise\\
    Who shall melt and who shall dance\\
    On the thin floor of life?
\end{Verse}


\chapter{Parcel}
\begin{Verse}
    Wherever may I find my body wandering and where I lay my hand\\
    A lone and unknown land\\
    Just follows me and never leaves\\
    Oh when has this begun?\\

    To them I say let there be \\
    a land I know and love\\
    and not the parcel nature gave\\
    to spare with me alone.
\end{Verse}


\chapter{Rolls}
\begin{Verse}
    An old typewriter lies on the desk\\
    Rolls of types and rolls of life\\
    the impression of a hot coffee\\
    on a cloudy morning\\
    and the prints of a dead hand.\\
    Oh young age, regret and retribution\\
    The keys' noise covers my thought\\
    and the noise that I bear inside.
\end{Verse}


\chapter{Friction}
\begin{Verse}
    Friction\\
    Friction\\
    Metal scraping\\
    Glass beheading\\
    Where we’re heading?\\
    Sleep and\\
    tick and\\
    turn and\\
    twist and \\
    walk and\\
    sit, for what?\\
    Desist?\\
    Your calculations\\
    fail.
\end{Verse}


\chapter{Machines}
\begin{Verse}
    Polygons of vision\\
    A field of empty vectors\\
    Directed to imperfection\\
    Escape your judgment\\
    Machines of flesh\\
    Which make machines\\
    For this you see\\
    'tis what thee be.
\end{Verse}


\chapter{OK}
\begin{Verse}
    Ok\\
    Why?\\
    OK\\
    What does it mean?\\
    What do you mean?\\
    This is ridiculous\\
    Ok\\
    The alarm is sounding\\
    Ok\\
    For well you see the waste this\\
    all\
    be\\
    O\\
    K.
\end{Verse}


\chapter{Masters of Doubt}
\begin{Verse}
    Do you feel good?\\
    Do you feel fine?\\
    What must be word\\
    that you make so flag of yourself\\
    When you proceed\\
    To bury the dead.
\end{Verse}


\chapter{Second Line}
\begin{Verse}
    Buffer of thought\\
    Distilled and saw\\
    It keeps bouncing inside\\
    Until you drown it in fire.
\end{Verse}


\chapter{Steam}
\begin{Verse}
    Steam, fire, electricity\\
    Some machines feed on it\\
    Some machines die on it\\
    All walk on the ribbon\\
    It goes extremely wide.
\end{Verse}


\chapter{Imaginary}
\begin{Verse}
    Flow\\
    Fly\\
    In the sky\\
    Slowly tired\\
    Not explored anything\\
    Neither being admired\\
    But still\\
    You may try.
\end{Verse}
\chapter{Sweden}
\begin{Verse}
    What shall say thee?\\
    2418\\
    Walk to the beam\\
    Shines so lightly\\
    Moves so brightly\\
    When you’ll think then\\
    Don’t complain me\\
    For what I see\\
    Is the most wide sea.
\end{Verse}

\chapter{Contempt}
\begin{Verse}
    Acknowledge it!\\
    Acknowledge it yourself\\
    The forces that behind you\\
    are pushing your contempt\\
    You see someone up there\\
    but no-one but yourself\\
    You think the freest free is what\\
    the heat has quickly fled\\
    No intention to assimilate\\
    let alone to adjudicate\\
    The superstructure of your thought\\
    is laid upon bones.
\end{Verse}


\chapter{Resonance}
\begin{Verse}
    Glaring eyes to the public\\
    you notice something:\\
    an entity which resonates\\
    the same frequency as you\\
    Be sure as well to keep in phase\\
    that’s what you’re going to do\\
    because if not you know that, too\\
    you’ll cancel whole in two.
\end{Verse}

\chapter{Beat}
\begin{Verse}
    Beat him!
    No, don’t despair\\ 
    There’s always a second place for losers,\\
    that’s hell\\
    Beat her!\\
    Look at your foe in the eyes\\
    You might both as well call it a tie\\
    For in this fight the only winner is who doesn't cry.\\
    Was that anytime?\\
    Well, everyone stops fighting when they die.
\end{Verse}

\chapter{Walk}
\begin{Verse}
    Walk downtown,\\
    looking around\\
    The movement, the sound\\
    The rubble on the ground\\
    changing\\
    slowly chaining\\
    Men walking in the snow\\
    Where do they go?\\
    What do they know?\\
    A solitary chimney\\
    Is coughing up some smoke\\
    You sit on the edge of the plane\\
    Which separates from them all.
\end{Verse}

\chapter{Act}
\begin{Verse}
    A close call\\
    It’s ringing\\
    You might as well pick up your phone\\
    Oh, look, it’s your friend\\
    He’s asking what you’ve done\\
    Interact is all you do,\\
    It flows inside everyone and all\\
    What did you make of it?
\end{Verse}

\chapter{Bell}
\begin{Verse}
    Rain and Snow\\
    Outside a shell of shells\\
    So while outside it’s cold as hell\\
    You ring the bell, for dinner’s served\\
    However don’t rejoice so much\\
    because you it’s not for you to know\\
    what then you’ll tell.
\end{Verse}

\chapter{Blue}
\begin{Verse}
    Looking in the eyes\\
    the broadcast just begun\\
    for there's some connection\\
    which requires no waveform\\
    oscillators dance, that's sure\\
    but what might they do\\
    when the only station I am tuning in\\
    is you.
\end{Verse}

\chapter{Red}
\begin{Verse}
    What Irony of a substance,\\
    powering such squalor\\
    mess of cogs and sweat\\
    But when the oil leaks\\
    the pain deceives\\
    that friction's gone.\\
\end{Verse}

\chapter{Casino}
\begin{Verse}
    Wait\\
    This game is rigged!\\
    What did you expect?\\
    Someone's gonna have to finance\\
    heaven and hell.
\end{Verse}

\chapter{War}
\begin{Verse}
    Go away and come\\
    command\\
    sustain\\
    engage\\
    and train\\
    terrain\\
    TERRAIN\\
    TERRAIN!
\end{Verse}

\chapter{Trees}
\begin{Verse}
    Hands in air\\
    fog is there\\
    dark and light\\
    all perspires\\
    when you're there.
\end{Verse}

\chapter{Violet}
\begin{Verse}
    Violet, light blue\\
    you know the\\
    address, too\\
    the corners of\\
    the world are\\
    shining there\\
    for you.\\
    Even when your soul denies\\
    you're bound\\
    by what's outside.
\end{Verse}


\chapter{Reflection}
\begin{Verse}
    Eyes stare at\\
    eyes\\
    The same soul inside\\
    yet shall we say\\
    we feel afraid, insane.
\end{Verse}


\chapter{Smile}
\begin{Verse}
    A symile of smiles, emerged\\
    from what seemed\\
    like crying.\\
    Despair may be\\
    a pretty fun affair.
\end{Verse}

\chapter{Tear}
\begin{Verse}
    Tear, torn, cut apart\\
    select your product from\\
    the list\\
    a little scalpel\\
    may fix that\\
    but what lays on the floor\\
    is hard to reattach 
\end{Verse}

\chapter{Void}
\begin{Verse}
    Beyond black\\
    beyond white\\ 
    beyond cubes\\
    beyond lights\\
    beyond love\\
    beyond lies\\
    it's not just what\\
    hearth and mind deny\\
    it's what thy were\\
    and thy shall be.
\end{Verse}

\chapter{Dust}
\begin{Verse}
    Writings on a wall\\
    a tree and its\\
    snow\\
    What acheivement do you keep\\
    in your mind and in your soul?\\
    Many speakers of all minds\
    fly and dance will\\
    tonight\\
    While the dust settles\\
    inside.
\end{Verse}

\chapter{Buyeth}
\begin{Verse}
   To everybody's contempt\\
   today is the event\\
   The day when you must pay\\
   for the uncherished bliss\\
   we all have been denying\\
   before it was taken by\\
   fire.
\end{Verse}

\chapter{Gates}
\begin{Verse}
   Bad,unjust\\
   war and lust\\
   we shall decide\\
   what you be must\\
   Dancing as a dancer\\
   Sleeping as a sleepr\\
   Heat,\\
   speeding cars,\\
   metal and wooden planks\\
   Your nature shall not stand\\
   where we not demand.
\end{Verse}

\chapter{Sweat}
\begin{Verse}
    Brick and bells\\
    On which an old man leans\\
    Not tired by age,\\
    but by life's appeal\\
    For who lives in a dream is sleeping\\
    and thus he's keeeping\\
    his life of sweat.
\end{Verse}

\chapter{Tin}
\begin{Verse}
    Laying on a bed in a late early after noon\\
    The pitch black and the tense muscles\\
    The will to grip to the comfy cushion yet the urge to act\\
    The incessant\\ time\\ awaits\\ one's\\ alarm.\\
    Laying inert like tin battles with the soul\\
    Until one wins on his own terms
\end{Verse}

\chapter{Stereo}
\begin{Verse}
    The downhill pipe\\
    all leaks and all flows\\
    jets and steamy puffs\\
    shielded and shivering\\
    break and set fire\\
    collide and deny\\
    barricade\\
    Don't fade, don't regret\\admire\\desire\\
    but rageous be \\  
    against the passage of the time.\\
    Flames shall be your soul\\
    and your touch shall be fire.\\
    Intertia and hiding\\
    only stack yourself\\
    up your back.
\end{Verse}

\chapter{Alley}
\begin{Verse}
    Shelf\\
    void and book and shelf\\
    and laughter and cry and joy and pain\\
    throughs books and shelves\\
    to read the mess\\
    away, far away\\
    it tangles in itself.
\end{Verse}

\chapter{Light}
\begin{Verse}
    Good little sky\\
    the bruising of the night is silent and shy\\
    you flucutate over the land of the tired\\
    which all contend.\\
    Oh, apprehend\\
    the solitary smoke\\
    which comes from the fire\\
    which burns in the pond\\
    of tomorrow's light.\\
    And when the vastness open their eyes\\
    do not deny\\
    the burns of light.
\end{Verse}

\chapter{Explode}
\begin{Verse}
    Time washes streaming through\\
    mind and soul to cleanse the bowl\\
    to which it fails, it does again,\\
    the rage subdues, the sight restrains\\
    in the vast field of which we are made.
\end{Verse}

\chapter{Again}
\begin{Verse}
Calmly and slowly\\
methodically inquiring\\
perfecting, note-taking\\
the plain of life is the battle field\\
on which the players move their \\little \\plastic \\ figures\\
Again and again\\
On the brink of war\\
You never truly wash them away\\
For they come in waves, back and forth\\
The stasis long, but the tempest strong\\
Irrupts in your home\\
and shatters it in tiny cardboard pieces\\
Again and again\\
So you walk alone in a calm windy night\\
chill for your hands but not enough for your soul\\
\end{Verse}
\clearpage
\begin{Verse}
and whatever path you choose\\
you swing your arms and you speed your pace\\
to outrun and trick the rain,\\
but through the intricacies of life\\
in spite of reason and disdain\\
the painful drops fall through the ground\\
to be collected in your veins\\
And all the parties you chill at\\
all the calls you pick up or dial in\\
each keystroke\\
each click\\
consumes the sky\\
in which you walk\\
in this sunny night.\\
Again and Again.
\end{Verse}

\chapter{Flow}
\begin{Verse}
Bitter and toxic \\
may well be\\
the sweet relief\\
to occam's seam.\\
You hug on your sofa\\
the insanity of a morning coffee\\
which just left you alone\\
in a puddle of mud\\
after much tribulation and desperate objectives\\
you're happy, sad, relieved, deceived\\
it is enough to let the flow\\
spill on the ground\\
at sunset's noon.
\end{Verse}
\chapter{Night}
\begin{Verse}
I am alone under a night sky with empty eyes,\\
a deafening silence,\\
and a cold face\\
bleeding in the pond of my life\\
knives contend\\
the supper chimes.
\end{Verse}
\chapter{The backrooms}
\begin{Verse}
Here are the backrooms\\
again.\\
The palpable shadow\\
just melts in thin air.\\
The vortex of people that\\
fly here and there.\\
The flicker of the neon lights\\
gets\\
in\\
the\\
soul\\
and all is rare\\
in the empty void\\
I hare\\
but never move.
\end{Verse}
\chapter{Cointainerland}
\begin{Verse}
An industrious shipyard\\
in a lonely field\\
behind a modest platform\\
sudbdues the sight\\
as the hot metal travels in the windows\\
and scrapes away the thoughts\\
of a moist summer day\\
spent on a plastic seat.
\end{Verse}
\chapter{Stormy light, Permanently night}
\begin{Verse}
It's day.\\
And I won't do anything.\\
The metal cuts the sky.\\
And I shan't do anything.\\
It's  permanently night.\\
Would I do anything?\\
Souls rain by an upper bridge, on a stormy city train.\\
Would I still do anything?\\
They're blending or they might.\\
And I should do anything?\\
A boat is sailing by\\
all the symbols that inspire.\\
Here is not all alike.\\
I shall do anything.\\
Tonight.\\
No time.
\end{Verse}
\chapter{Feedom standings}
\begin{Verse}
The sparkling taste\\
of the\\
august air\\
conditioning\\
in a sweet-sour mall.\\
Raves the human fire in ice\\
 freest touches humanity whenstone and fire itself.\\
What freedom is the one to \\
void itself?\\
Ethics class in a fancy hotel\\
while the metal clangs\\
crushing the human flesh \\
under a green sky.
The mirrors hurt it\\
Glass breaks apart in the fashionable\\
ideological parade.\\
Where do you stand?
\end{Verse}
\chapter{Sliding Doors}
\begin{Verse}
Sliding doors\\
slide slaying\\
time laying down\\
the evil soul they\\
lie but retain\\
when they slide\\
in your face.\\
Nevermind.
\end{Verse}
\chapter{Boys?}
\begin{Verse}
The blushing heat of the soul\\
when the hugs touch the sky\\
and the night dwindles by\\
and burns the eyes of death\\
and kisses the fresh grass\\
that grows inside\\
my, my.
\end{Verse}
\chapter{Rest}
\begin{Verse}
Sleep\\
light\\
rest\\
mild, rage\\
quiet, moving fastly\\
on the tracks\\
never matters, what you try\\
inside.
\end{Verse}
\chapter{Mellowly}
\begin{Verse}
I see sparks of music and loud light\\
pierces the night\\
Familiar tunes of sugar-summers\\
sync the beat to the drumhead of my skin\\
To mix and flow in the sea\\
of various souls\\
that dance and flutter in the hot\\
summer cold.\\
But sitting on a chair, pondering the\\
square, enstranged I stay\\
and peer at the neon sky\\
to bear the weight of air\\
glazing around the ink\\
that scrapes the blood\\
on half-white page of the summer time.\\
Ethereal figures, meanwhile, float and dance\\
with mind-suspending gaze\\
zoom-in and standing up\\
to interrupt the crystal crowd\\
what is within enclosed blasts\\
and backwards I fly\\
in happy-desperate mellow silence.
\end{Verse}
\chapter{Petroleum}
\begin{Verse}
Sweet city petroleum jelly\\
Summer storming in and out\\
leading lead in office buildings\\
scribbling away some math\\
in my back pocket\\
to save it for later\\
this is my stop\\
catch me again\\
when the sun blazes\\
on the packed void\\
that i bear inside until\\
a good meal and a hug\\
clear me out and set me up\\
to live tonight.
\end{Verse}
\chapter{Proof}
\begin{Verse}
Proof, conjecture, demosntration,\\
theorem, lemma, corollary, definition\\
Prove me this to show me that\\
I am everything we are\\
our relationship is symmetric\\
but is it by any metric\\
proofed against the world's deceptions?\\
Would it be a misconception\\
If I state that $[a,b,c]$\\
$a)$ You have bored me to delirium\\
$b)$ I have loved you to hatred\\
$c)$ There is no sense ouside the empiric\\
so just hug me until we fade then.
\end{Verse}
\newpage\null\thispagestyle{empty}\newpage
\end{document}
